### 2019-06-18 doc/bilevel/paper.tex
Editing pessimistic formulation to include both the general version and the min max version, with the Wiesemann et al 2013 comparison of the two

\begin{equation}
\label{eqn:bilevel_pess}
\begin{array}{ll}
\min_{x \in X, y \in Y}   & F(x,y)\\
\st                 & G(x,y) \leq 0\\
                    & \forall y \in P(x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(x) & = & \argmin_{y \in Y}    & f(x,y)\\
 & &                            & g(x,y) \leq 0.
\end{array}
\]
This formulation ensures that the selection value for $y$ will in fact maximize $F(x,y)$; in other words, the upper-level problem must be feasible for all values $y$ including the least favorable outcome of the lower-level problem $P(x)$. Unless otherwise stated, the canonical bilevel problem in the subsequent examples will be derived from the \textit{optimistic} approach presented in \eqref{eqn:bilevel}.

>>>>

\begin{equation}
\label{eqn:bilevel_pess}
\begin{array}{lll}
\min_{x \in X}   & F(x)\\
\st                 & G(x,y) \leq 0 &\forall y \in P(x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(x) & = & \argmin_{y \in Y}    & f(x,y)\\
 & &                            & g(x,y) \leq 0.
\end{array}
\]
This formulation ensures that the upper-level problem is feasible for all values $y$ including the least favorable outcome of the lower-level problem $P(x)$. 
It is common to see the pessimistic problem written as
\begin{equation}
\label{eqn:bilevel_pess_minmax}
\min_{x \in X}\max_{y \in P(x)} H(x,y).
\end{equation}
Though formulation (\ref{eqn:bilevel_pess_minmax}) makes clear the selected value for $y$ will in fact maximize $H(x,y)$, note that it is actually less general than (\ref{eqn:bilevel_pess}) since we can rewrite it in the form of (\ref{eqn:bilevel_pess}), as
\[
\begin{array}{lll}
\min_{x, \tau} &\tau \\
\st & \tau \geq H(x, y) & \forall y \in P(x) \\
& x \in X,
\end{array}
\]
but it is not always possible to tranform problems in the form of (\ref{eqn:bilevel_pess_minmax}) to (\ref{eqn:bilevel_pess}) without definting functions $H(x,y)$ and $f(x,y)$ on the extended real line \cite{WiesemannTKR2013}.
Unless otherwise stated, the canonical bilevel problem in the subsequent examples will be derived from the \textit{optimistic} approach presented in \eqref{eqn:bilevel}.
